\documentclass[11pt,a4paper]{moderncv}

% moderncv themes
%\moderncvtheme[blue]{casual}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
\moderncvtheme[blue]{classic}                % idem

\usepackage[T1]{fontenc}
% character encoding
\usepackage[utf8x]{inputenc}                   % replace by the encoding you are using
\usepackage[portuguese]{babel}

% adjust the page margins
\usepackage[scale=0.8]{geometry}
\recomputelengths                             % required when changes are made to page layout lengths

\fancyfoot{} % clear all footer fields
\fancyfoot[LE,RO]{\thepage}           % page number in "outer" position of footer line
\fancyfoot[RE,LO]{\footnotesize } % other info in "inner" position of footer line

% personal data
\firstname{Gabriel}
\familyname{Candal}
\title{Curriculum Vitae}
\address{Porto, Portugal}
\mobile{(+351) 917 589 663}
\email{gabrielcandal@gmail.com}
\homepage{github.com/gcandal}
\extrainfo{linkedin.com/in/gcandal}
\extrainfo{Skype: g.candal}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\vspace{-10mm}

%Section
\section{Experience}
\vspace{-2mm}
\subsection{Working}
\cventry{Dez 2016-*}{Software Engineer}{\href{http://www.feedzai.com}{Feedzai}}{}{}
{}
\cventry{2015-2016}{Software Engineer}{\href{http://www.platforme.com}{PLATFORME International}}{}{}
{Joined as the 3rd developer a team that built a best of breed web 3D customiser,
integrating it with \href{https://www.farfetch.com/}{farfetch.com}, as well as
its own e-commerce engine. Individually, I have:
\begin{itemize}
  \item Contributed to all areas of our products, from the core
  customiser to the website's front and back-ends (including the e-commerce engine)
  \item Built an analytics dashboard
  \item Improved a platform for running and monitoring parallel image transformation tasks
  (with a 2-8x speedup when compared to its predecessor)
\end{itemize}
To do this I've used MongoDB, Python, HTML/CSS and Javascript (jQuery).
\newline Besides doing software development, I have also gathered requirements from internal and external
stakeholders and helped schedule and coordinate tasks within the technical team.
}
\cventry{2014-2015}{Co-Founder \& Lead Developer}{Trigonum}{}{}
{Responsible for the software development in a company focused on products for
health professionals. Used HTML/CSS, PHP, jQuery and PostgreSQL.}
\cventry{\small Jul-Aug \normalsize 2013}{Software Developer Intern}{\href{http://www.criticalmanufacturing.com/pt/homepage}{
Critical Manufacturing}}{}{}{Together with a colleague developed an
tool to assist developers in testing. Compared to the one previously used
it ran 5x faster, besides providing information
as structured XML and producing 3x smaller files. Used C++ on top of Solaris.}
\vspace{2mm}
\subsection{Teaching Assistant}
\cventry{\small Feb-May \normalsize 2015}{Programming + Algorithm Design and Analysis}{\href{http://www.fe.up.pt}{Faculty of Engineering of
the University of Porto}}{FEUP}{}{}
\cventry{\small Sep-Nov \normalsize 2014}{ProjetoFEUP}{\href{http://www.fe.up.pt}{Faculty of Engineering of
the University of Porto}}{FEUP}{}{}
\vspace{-3mm}

%Section
\section{Education}
\cventry{2011-2016}{Masters in Informatics and Computing Engineering}{\href{http://www.fe.up.pt/mieic}{Faculty of Engineering of
the University of Porto}}{FEUP}{}{}
\vspace{-3mm}

%Section
\section{Skills}
\cvline{Basic}{\small Haskell, Prolog, Docker, Spark}
\cvline{Built stuff with}{\small \textbf{General purpose} (Scala, Python, Java, C/C++, Ruby), \textbf{web} (Javascript, jQuery, node.js, AngularJS, Ruby on Rails, HTML/CSS, PHP), \textbf{databases} (PostgreSQL, MongoDB), \textbf{mobile} (Android), \textbf{other} (Unix, git, UML, algorithms, concurrency/multiprocessing, MapReduce)}
\vspace{-3mm}

%Section
\section{Projects}
\cvline{Actor Binary Tree}
{Made a distributed binary tree implementation based on Akka's actors as part of Martin Odersky's MOOC on reactive programming. \textbf{Scala, Akka}}
\cvline{GlinttSupport}
{In collaboration with \href{http://www.glintt.com/}{Glintt}, built a call-center-like website which aggregated Facebook and Twitter feeds of a given company, as well as a custom 1-on-1 chat, and presented them as unresolved issues for the operator to solve.  \textbf{AngularJS, node.js}}
\cvline{Interpreters}
{As a part of UW's MOOC on programming languages, built two interpreters: one for geometric expressions and the other for a MUPL (Made Up Programming Language, which was a subset of Racket which included higher-order functions). \textbf{StandardML, Racket}}
\cvline{\href{https://github.com/gcandal/DistributedBackup}{Distributed Backup}}
{Distributed and decentralized application that provides file backup capabilities, making use of UDP's unreliable message-passing. \textbf{Java}}
\cvline{\href{https://github.com/joaofloressantos/Regex_To_DFA}{Regex compiler}}
{A compiler from PCRE regex to a C++/Java program which matches that regex to user input, based on a validation via DFA. \textbf{Java}}
\cvline{\href{https://github.com/tiagoaf5/Beef}{Beef}}
{A betting website for football leagues. \textbf{jQuery, Ruby on Rails}}
\cvline{\href{https://github.com/augustocravosilva/CoastWeather}{CoastWeather}}
{Android app that provides a way for users to evaluate the weather at portuguese beaches with some social networking features. \textbf{PHP, Python, Android}}
\cvline{\href{https://github.com/gcandal/NeuralNetwork}{NeuralNet}}
{An OO implementation of a feed forward backpropagation neural network. \textbf{Java}}
\cvline{\href{https://github.com/gcandal/minixasteroid}{Asteroids}}
{A game which runs on top of Minix, which involved programming every devices' interface (timer, keyboard, mouse, VESA graphics). \textbf{C/C++}}
\cvline{\href{https://github.com/gcandal/JADETrustModels}{Trust}}
{Agent-based application to compare several trust model's behavior under different scenarios. \textbf{Java}}
\cvline{\href{https://github.com/MiguelGPereira/ViaVerde/blob/master/ViaVerde.vdmpp}{Via Verde}}
{A formal model for Portugal's highways toll system. \textbf{VDM++}}

%Section
\section{Extra Courses and Certificates}
\cventry{Jun 2015}{Principles of Reactive Programming}{\href{https://www.coursera.org/course/reactive}{Coursera}}{EPFL}{}{}
\cventry{Aug 2015}{CS190.1x: Scalable Machine Learning}{\href{https://www.edx.org/course/scalable-machine-learning-uc-berkeleyx-cs190-1x}{edX}}{BerkeleyX}{}{}
\cventry{Feb 2013}{CS169.1x Software as a Service I}{\href{https://www.edx.org/course/engineering-software-service-uc-berkeleyx-cs169-1x}{edX}}{BerkeleyX}{}{}
\cventry{Feb 2015}{CS169.2x Software as a Service II}{\href{https://www.edx.org/course/engineering-software-service-part-2-uc-berkeleyx-cs169-2x}{edX}}{BerkeleyX}{}{}
\cventry{Dec 2014}{Programming Languages}{\href{https://www.coursera.org/course/proglang}{Coursera}}{University of Washington}{}{}
\cventry{Mar 2015}{Algorithms: Design and Analysis, Part 1}{\href{https://www.coursera.org/course/algo}{Coursera}}{Stanford}{}{}
\cventry{May 2015}{Algorithms: Design and Analysis, Part 2}{\href{https://www.coursera.org/course/algo2}{Coursera}}{Stanford}{}{}
\cventry{Nov 2013}{Functional Programming Principles in Scala}{\href{https://www.coursera.org/course/progfun}{Coursera}}{EPFL}{}{}
\cventry{May 2014}{Certificate in Advanced English}{University of Cambdrige}{}{}{}
\cventry{Dec 2014}{FP101x Introduction to Functional Programming}{\href{https://www.edx.org/course/introduction-functional-programming-delftx-fp101x}{edX}}{DelftX}{}{}
\cventry{Oct 2014}{M101JS: MongoDB for Node.js Developers}{\href{https://university.mongodb.com/courses/M101JS/about}{MongoDB, Inc.}}{}{}{}
\cventry{Jul 2015}{CS100.1x: Introduction to Big Data with Apache Spark}{\href{https://www.edx.org/course/introduction-big-data-apache-spark-uc-berkeleyx-cs100-1x}{edX}}{BerkeleyX}{}{}
\cventry{2013-*}{13 other MOOCs}{Coursera, edX and Udacity}{}{}{}
\vspace{-3mm}

%Section
\section{Other}
\cvline{Open-source}{\small moviepy, budy-api, blockly-generator-csharp}
\cvline{Volunteer}{\small DotA-League's Junior Admin, Codecademy, INForum 2014, Talk A Bit's 4th edition}
\cvline{Author}{\small \href{http://nextcommit.github.io/}{Next Commit}}
\cvline{Sports}{\small Goju-ryu karate, football}

\end{document}
